Buildtime Trend

### 2016-01-29 buildtimetrend/btt_fosdem2016.tex
update future roadmap
move description and demo slides

      \item caching for badges and dashboard charts
      \item support private Github repos

@@

      \item more and improved metrics and trends

@@

      \item Dashboard : \href{https://buildtimetrend.herokuapp.com/dashboard/buildtimetrend/python-lib/index.html}{\small{https://buildtimetrend.herokuapp.com/dashboard/buildtimetrend/python-lib}}

>>>>

      \item more and improved metrics and charts
      \item improve navigation and searching on dashboard

@@

      \item notification on a jumpy build job

@@
